NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-11-30 ms_nihao_budget.tex
final version for third submission

\author[Wang et al.]{Liang Wang$^{1,3}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
  Gregory S. Stinson$^3$, Andrea V. Macci\`o$^{2,3}$, 
\newauthor{Thales Gutcke$^3$, Xi Kang$^1$}\\
$^1$Purple Mountain Observatory, the Partner Group of MPI f\"ur Astronomie, 2 West Beijing Road, Nanjing 210008, China\\
$^2$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
\begin{document}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 5\times10^6$K), and hot gas (T$> 5\times10^6$K)
  , inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes are missing baryons. The missing mass
  has been relocated past 2 virial radii, and cool gas dominates
    the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
    while the  warm-hot gas dominates at high mass (M$_{200}
    \gta 3 \times 10^{11} \Msun$).  Haloes of mass $\Mhalo\sim
  10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.  More
  massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher fraction
  of their baryons, with $\sim 30\%$ missing, consistent with recent
  observational estimates.  Moreover, these more massive haloes
    reproduce the observed  fraction of cold, warm-hot and hot gas.
    The fraction of cool gas we predict (0.11) is significantly lower
    than the observation from COS-HALOs (0.3-0.47), but agrees with
    the alternative analysis of \citet{Stern16}.
\end{abstract}

@@

{\bf As a part of the IGM, the circum galactic medium (CGM) is always 
treated as }an major potential
reservoir of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to detect
cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
substantial  portion of the CGM is in the warm or hot phase with
temperature T $> 10^{4.5}$ K.  Gas enters this phase through
photoionization, accretion shocks or shocks caused by galactic winds
\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
the detection is dominated by metal lines, e.g. \ovi{}.  Recent
advances in the detection of gas in the CGM have come  from the COS
survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
significant amount of warm ($10^4 < T <5\times 10^6$K) gas has been detected
\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
future such observations will be extended to a wider range of halo
masses.  A number of large volume cosmological simulations
\citep{Ford13, Ford15, Suresh15b, Oppenheimer16} and zoom-in
cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
given  predictions for the \hi{} and \ovi{} absorption
line. \citet{Gutcke16} compared the column density profile of \ovi{}
and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
cosmological hydrodynamical simulation suite with observations,
studied the covering fraction of dense \hi{}, looked at the shape of
the CGM and its chemical composition. The simulations
  reproduce  the observational covering fraction and column density
  profile of cool \hi{} well, and recover the observed trends of
  \ovi{} column density with luminosity and impact parameter. In
  common with other simulations, however, the column density of \ovi{}
  is lower and the extent of optically thick \hi{} is smaller than
  observed.

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
\citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift $z \approx 0.5-2$ remove a large
amount of gas from the halo. {\bf Several simulations 
\citep{Crain10, Christensen16,Voort16}} found the baryon fraction
and gas fraction are reduced compared to the cosmic baryon
fraction, especially in low mass haloes.
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project.  Reproducing the stellar mass content in dark matter haloes
both today and in the past has been a formidable challenge for
cosmological galaxy formation simulations \citep{Weinmann12,
  Hopkins14}. Even the latest state-of-the art simulations have
trouble: the ILLUSTRIS simulation \citep{Vogelsberger14} strongly
overpredicts the stellar masses in dwarf galaxy haloes $(M_{200} \lta
10^{11}\Msun)$, while the EAGLE simulations \citep{Schaye15}
underpredict the peak of the star formation efficiency in halos of
mass $M_{200}\sim 10^{12}\Msun$. In contrast, the NIHAO galaxies are
consistent with the stellar mass vs halo mass relations from halo
abundance matching since redshift $z\sim 4$ \citep{Wang15}, the galaxy
star formation rate vs stellar mass relation since $z\sim 4$
\citep{Wang15}, and the cold gas mass vs stellar mass relation at
$z\sim 0$ \citep{Stinson15}.  Therefore, the simulations make
plausible predictions for the mass fractions and physical locations of
the warm and hot gas components.  We find that all the haloes contain
less baryons than expected according to the cosmic baryonic fraction,
but the missing fraction is strongly mass dependent.

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project
\citep{Wang15}.   The initial conditions are created to keep the same
numerical resolution across the whole mass range with typically a
million dark matter particles inside the virial radius of the target
halo at  redshift $z=0$.  The halos to be re-simulated at higher
resolution with baryons have been extracted from 3 different pure
N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.  
{\bf Dark matter particle masses range from $\sim 10^3 \Msun$ in 
our lowest mass haloes to $\sim 10^5 \Msun$ in our most massive 
haloes, and their force softenings range from $\sim$ 100 pc in 
low mass range to $\sim$ 900 pc in high mass range.
Gas particles are less massive in factor of 5 correspondingly, and
the force softenings are 3 times less than dark matters.}
More information on the collisionless parent simulations, the force
  softenings and particle masses for the highest refinement level for
  each simulation and sample  selection can be found in
\citet{Dutton14} and \citet{Wang15}.

@@

%% FIGURE 1
\begin{figure}
\centerline{
  \psfig{figure=barbudget_linearlog.eps,width=0.48\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations  as a
  function of halo mass. The green points show the ratio between the
  baryonic mass (stars + gas) inside the virial radius and the total
  baryonic mass associated with the dark matter halo. The blue points
  show the corresponding fraction for the stars. The solid green line
  and shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons, and the power-law nature of the relations,
  respectively.}
\label{fig:budget}
\end{figure}

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budget_res.eps,width=0.85\textwidth}
}
\caption{{\bf Linear fractional baryon content of NIHAO
simulations as a function of halo mass color coded by
number of dark matter particles per halo.}}
\label{fig:budget_res}
\end{figure*}

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
}
\caption{Comparison between baryon (upper panels) and stellar
    fractions (lower panels) in the NIHAO simulations (blue circles)
    with simulations from \citet{Voort16} (left, red pentagons) and
    \citet{Christensen16} (right, purple pentagons).}
\label{fig:fire_com}
\end{figure*}

@@

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass {\bf within 20\% $\Rvir$} (blue points), 
and the total baryonic
mass including stellar mass plus gas mass (green points).  For the
stellar mass fraction we also show the relations from the halo
abundance  matching \citep{Moster13, Behroozi13, Kravtsov14}.  The
grey area is the one sigma scatter around the mean value  from
\citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all haloes in
our study contain less than the universal fraction of baryons. The
upper panel uses a linear y-axis scale, which highlights the large
amount of baryons that are missing, especially in low mass haloes. The
logarithmic scale in the lower panel highlights the power-law nature
of the relations.

@@

Since most of the haloes we study are above the mass where the cosmic
UV background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons. 
  This is consistent with expectations from energy driven gas
  outflows, where the lower star formation efficiency is more than
  compensated by the shallower potential wells of lower lower mass
  halos according {\bf to} the mass loading factor and circular velocity 
  {\bf relation }$\eta \propto V^{-2}$
   \citep[e.g.,][]{Dutton12, Christensen16}.

@@

Fig.~\ref{fig:budget_res} shows the budget fraction of cold, 
cool and warm-hot gas fraction. Since one can imagine that 
with increased resolution, higher densities can be achieved in the
CGM, potential leading to more cooling and larger
cold/cool gas fraction, all the points are color coded by 
the total number of dark matter particles within the haloes.
In the plot, the number of dark matter
partilce per halo spans 2 magnitudes and has no correlation 
with cold and cool gas fraction.
Therefore, the baryonic fractions predicted by NIHAO simulations
are convergent.

@@

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes,
{\bf and is a radius within the effective volume of the simulations
since contamination fraction in a shell between 0.9 and 
1.0 $\Rbar$ shows most NIHAO galaxies have a fraction close to 0,
with largest only around 10 - 20. }
Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
function of the virial mass. In physical units, we find that the
baryon radius generally increases with virial mass. When
  normalized by the virial radius, the distance baryons are ejected
  gradually decreases as halo mass increases, varying from
  $\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$
  to $\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.

@@

In Fig.~\ref{fig:inout}, we show the mass fractions of gas (in three
phases) inside the virial radius (filled blue points) and between the
virial and baryon radius (open red points)
{\bf which are relative to the fiducial baryonic mass within the 
virial radius}.
%
The fractions of cold gas,
$f_{\rm cold}$, are shown in the left panel.  Inside the
virial radius $f_{\rm cold}$ increases gradually from zero at a halo
mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo mass of
$10^{12}\Msun$.  The gas outside the virial radius has the opposite
and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of mass
$10^{10}\Msun$ and decreases to zero by halo masses of
$10^{11}\Msun$.
%
The fractions of cool gas, $f_{\rm cool}$, are
shown in the middle panel.  Inside the virial radius, $f_{\rm
  cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
and declines to less than 10\% below and above halo masses of
$10^{10}\Msun$ and $10^{12}\Msun$, respectively.  For most haloes there
is more cool gas outside than inside the virial radius.  In haloes
of mass $10^{10}\Msun$, $f_{\rm cool}\sim 80\%$, and decreases to
less than 10\% by a halo mass of $10^{12}\Msun$.
%
The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
right panel.  The trends of the gas inside and outside the virial
radius are quite similar, $f_{\rm warm}$ increases monotonically with
halo mass with maximum values of $\sim 30\%$.
%
The hot gas isn't shown since it is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo masses in the range
$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
associated with the dark matter halo are in the cold and cool phases,
and are located well outside of virial radius.  For haloes in the mass
range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
gas, cool gas and  warm-hot gas are comparable.

@@

The COS-HALOs survey is filling in details about the CGM at low
redshift \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13,
  Werk14}.  For the CGM of low-redshift $\sim L^*$ galaxies
($\Mstar\sim 10^{10.5}\Msun$), \citet{Tumlinson13} and
\citet{Peeples14} constrain the mass of  the warm-hot CGM ($T \sim
10^{5-6.7}$K), \citet{Werk14} provides a strict lower limit to the mass
of cool material ($T \sim 10^{4-5}$K) in the CGM of these galaxies.
In a study using X-rays, \citet{Anderson13} place a constraints on the
mass of  hot gas ($T > 5\times10^6$K) residing in the extended hot halos.
These observational constraints are shown in Fig.~\ref{fig:comparison}
with the same colour scheme as in Fig.11 of \citet{Werk14}.  The
stellar mass fractions are based on halo abundance matching as
described in \citet{Kravtsov14}, while the cold disk gas mass comes
from \citet{Dutton11}.
{\bf In addition, since \citet{Crain10} and \citet{Voort13} show that 
soft X-ray emission traces gas with temperatures a few times the 
virial temperature (T$_{\rm vir} = 10^6$ K for M$_{200} \sim 
10^{12} \Msun$), we also estimate the hot gas fraction with lower
boundaries ($3\times 10^6$ K and $10^6$ K) between the hot gas and 
warm-hot gas, the fractions can increase to 0.00511 ($3\times 10^6$K) 
and 0.04168 ($10^6$ K).}
{\bf The mean value of missing fraction is the residual fraction
of the sum of mean values of all components fractions in unity
and the lower and upper limits are calculated in the same manner
by the upper and lower limits of the all fractions.}

%% FIGURE 7
\begin{figure*}
\centerline{
  \psfig{figure=budget.eps,width=0.8\textwidth}
}
\caption{Baryonic budget  of NIHAO haloes of mass $3.5\times 10^{11} <
  M_{200}/\Msun < 3.5 \times 10^{12}$ (blue points  with 1$\sigma$
  error bars) compared with observations of  $M_{200} \sim
  10^{12}\Msun$ haloes (shaded regions). There is good agreement,
  except for the cool gas which has two conflicting measurements:
  \citet[][upper]{Werk14} upper, \citet[][lower]{Stern16}.  }
\label{fig:comparison}
\end{figure*}

>>>>

\author[Wang et al.]{Liang Wang$^{1,3,4}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
  Gregory S. Stinson$^3$, Andrea V. Macci\`o$^{2,3}$, 
\newauthor{Thales Gutcke$^3$, Xi Kang$^1$}\\
$^1$Purple Mountain Observatory, the Partner Group of MPI f\"ur Astronomie, 2 West Beijing Road, Nanjing 210008, China\\
$^2$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
$^4$International Centre for Radio Astronomy Research (ICRAR)
, M468, University of Western Australia, 35 Stirling Hwy, Cr
awley, WA 6009, Australia}
\begin{document}

@@

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 5\times10^6$K), and hot gas (T$>
  5\times10^6$K), inside the virial radius, $R_{200}$.  Compared to
  the predicted baryon mass, using the dark halo mass and the
  universal baryon fraction, $f_{\rm b}\equiv \Omega_{\rm
    b}/\Omega_{\rm m}=0.15$, we find that all of our haloes are
  missing baryons. The missing mass has been relocated past 2 virial
  radii, and cool gas dominates the corona at low mass (M$_{200} \lta
  3 \times 10^{11} \Msun$) while the  warm-hot gas dominates at high
  mass (M$_{200} \gta 3 \times 10^{11} \Msun$).  Haloes of mass
  $\Mhalo\sim 10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.
  More massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher
  fraction of their baryons, with $\sim 30\%$ missing, consistent with
  recent observational estimates.  Moreover, these more massive haloes
  reproduce the observed  fraction of cold, warm-hot and hot gas.  The
  fraction of cool gas we predict ($0.11\pm0.06$) is significantly
  lower than the observation from COS-HALOs (0.3-0.47), but agrees
  with the alternative analysis of \citet{Stern16}.
\end{abstract}

@@

{\bf As a part of the IGM, the circum galactic medium (CGM) is always 
treated as }an major potential
reservoir of the missing baryons. \hi{} and metal absorption lines are
expected  to signpost such diffuse baryonic content. \hi{} is mainly
from gas with temperature T $\sim 10^4$ K so that it is able to detect
cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
substantial  portion of the CGM is in the warm or hot phase with
temperature T $> 10^{4.5}$ K.  Gas enters this phase through
photoionization, accretion shocks or shocks caused by galactic winds
\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
the detection is dominated by metal lines, e.g. \ovi{}.  Recent
advances in the detection of gas in the CGM have come  from the COS
survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
significant amount of warm ($10^4 < T <5\times 10^6$K) gas has been detected
\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
future such observations will be extended to a wider range of halo
masses.  A number of large volume cosmological simulations
\citep{Ford13, Ford16, Suresh15, Oppenheimer16} and zoom-in
cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
given  predictions for the \hi{} and \ovi{} absorption
lines. \citet{Gutcke16} compared the column density profile of \ovi{}
and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
cosmological hydrodynamical simulation suite with observations,
studied the covering fraction of dense \hi{}, looked at the shape of
the CGM and its chemical composition. The simulations
  reproduce  the observational covering fraction and column density
  profile of cool \hi{} well, and recover the observed trends of
  \ovi{} column density with luminosity and impact parameter. In
  common with other simulations, however, the column density of \ovi{}
  is lower and the extent of optically thick \hi{} is smaller than
  observed.

The physical properties of the CGM has been shown to be able to
test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
predicted galactic halo baryon fractions of galaxies with halo
masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
cosmological hydrodynamical simulations with a well-constrained
model for galactic outflows.  They found that, without the outflow
model, the baryon fraction inside the virial radius is roughly the
cosmic baryonic fraction, but with the outflow model, the baryon
fraction is increasingly suppressed in lower mass haloes.  By
comparing results at $z=3$ and $z=0$, they showed that large
haloes remove their baryons at early times while small haloes lose
baryons more recently due to the wind material taking longer to
return to low-mass galaxies than high-mass galaxies.
\citet{Muratov15} showed similar results that the gas and
baryon fractions are lower at lower redshift, after powerful
outflows at intermediate redshift $z \approx 0.5-2$ remove a large
amount of gas from the halo. {\bf Several simulations 
\citep[e.g.,][]{Crain10, Christensen16,Voort16}} found the baryon fraction
and gas fraction are reduced compared to the cosmic baryon
fraction, especially in low mass haloes.
%  
\citet{Sokolowska16} studied the halo gas of three Milky way-sized
galaxies using cosmological zoom-in simulations. They found that
most of missing baryons actually resides in warm-hot and hot gas
which contribute to 80\% of the total gas reservoir.  The recovered
baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
is sensitive to the feedback model so that a reliable spatial
mapping of the warm-hot medium will provide  a stringent test for
feedback models.

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project.

Reproducing the stellar mass content in dark matter haloes
both today and in the past has been a formidable challenge for
cosmological galaxy formation simulations \citep{Weinmann12,
  Hopkins14}. Even the latest state-of-the art simulations have
trouble: the ILLUSTRIS simulation \citep{Vogelsberger14} strongly
overpredicts the stellar masses in dwarf galaxy haloes $(M_{200} \lta
10^{11}\Msun)$, while the EAGLE simulations \citep{Schaye15}
underpredict the peak of the star formation efficiency in halos of
mass $M_{200}\sim 10^{12}\Msun$. In contrast, the NIHAO galaxies are
consistent with the stellar mass vs halo mass relations from halo
abundance matching since redshift $z\sim 4$ \citep{Wang15}, the galaxy
star formation rate vs stellar mass relation since $z\sim 4$
\citep{Wang15}, and the cold gas mass vs stellar mass relation at
$z\sim 0$ \citep{Stinson15}.  Therefore, the simulations make
plausible predictions for the mass fractions and physical locations of
the warm and hot gas components.  We find that all the haloes contain
less baryons than expected according to the cosmic baryonic fraction,
but the missing fraction is strongly mass dependent.

@@

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project
\citep{Wang15}.   The initial conditions are created to keep the same
numerical resolution across the whole mass range with typically a
million dark matter particles inside the virial radius of the target
halo at  redshift $z=0$.  The halos to be re-simulated at higher
resolution with baryons have been extracted from 3 different pure
N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}.   {\bf Dark
  matter particle masses range from $\sim 10^{4} \Msun$ in  our lowest
  mass haloes to $\sim 10^{6} \Msun$ in our most massive  haloes, and
  their force softenings range from $\sim$ 150 pc to $\sim$ 900 pc,
  respectively Gas particles are less massive by factor of
  $(\Omega_{\rm dm}/\Omega_{\rm b})\simeq 5.48$, and  the
  corresponding force softenings are 2.34 times smaller.}  More
information on the collisionless parent simulations, the force
softenings and particle masses for the highest refinement level for
each simulation and sample  selection can be found in \citet{Dutton14}
and \citet{Wang15}.

@@

%% FIGURE 1
\begin{figure}
\centerline{
  \psfig{figure=barbudget_linearlog.eps,width=0.46\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations  as a
  function of halo mass. The green points show the ratio between the
  baryonic mass (stars + gas) inside the virial radius and the total
  baryonic mass associated with the dark matter halo. The blue points
  show the corresponding fraction for the stars. The solid green line
  and shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons, and the power-law nature of the relations,
  respectively.}
\label{fig:budget}
\end{figure}

@@

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass {\bf within 20\% $R_{200}$} (blue
points),  and the total baryonic mass including stellar mass plus gas
mass (green points).  For the stellar mass fraction we also show the
relations from halo abundance  matching \citep{Moster13, Behroozi13,
  Kravtsov14}.  The grey area is the one sigma scatter around the mean
value  from \citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all
haloes in our study contain less than the universal fraction of
baryons. The upper panel uses a linear y-axis scale, which highlights
the large amount of baryons that are missing, especially in low mass
haloes. The logarithmic scale in the lower panel highlights the
power-law nature of the relations.

@@

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budget_res.eps,width=0.95\textwidth}
}
\caption{{\bf Baryon content of NIHAO simulations as a function of
    halo mass color coded by number of dark matter particles per
    halo. This shows the stars and gas content of the simulations is
    insensitive to order of magnitude changes in particle
    resolution.}}
\label{fig:budget_res}
\end{figure*}

Since most of the haloes we study are above the mass where the cosmic
UV background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons.  This
is consistent with expectations from energy driven gas outflows, where
the lower star formation efficiency is more than compensated by the
shallower potential wells of lower mass halos according {\bf to} the
mass loading factor and circular velocity  {\bf relation }$\eta
\propto V^{-2}$ \citep[e.g.,][]{Dutton12, Christensen16}.

@@

{\bf Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
  and warm-hot gas color coded by the number of dark matter particles
  inside the virial radius. Since one can imagine that with increased
  resolution, higher densities can be achieved in the CGM, potential
  leading to more cooling and larger cold/cool gas fractions.  In our
  simulations we find no dependence of stars and gas fractions with particle
  number, indicating these quantities are not sensitive to numerical
  resolution using the NIHAO sub-grid model.}

%% FIGURE 3
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
}
\caption{Comparison between baryon (upper panels) and stellar
    fractions (lower panels) in the NIHAO simulations (blue circles)
    with simulations from \citet{Voort16} (left, red pentagons) and
    \citet{Christensen16} (right, purple pentagons).}
\label{fig:fire_com}
\end{figure*}

@@

To estimate how far the baryons escape, we measured the radius,
$\Rbar$, within which the total baryon mass equals the fiducial
baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
the true extent of the missing baryons since the baryon mass includes
gas and stars that belong to nearby lower mass haloes.  {\bf It is a
  radius within the high-resolution volume of the simulations since
  the contamination fraction in a shell between 0.9 and  1.0 $\Rbar$
  shows most NIHAO galaxies have a fraction close to 0, with largest
  only around 10 - 20\%. } Fig.~\ref{fig:missvr} shows the baryon
radius of each galaxy as function of the virial mass. In physical
units, we find that the baryon radius generally increases with virial
mass. When normalized by the virial radius, the distance baryons are
ejected gradually decreases as halo mass increases, varying from
$\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$ to
$\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.

@@

In Fig.~\ref{fig:inout}, we show the mass fractions of gas (in three
phases) inside the virial radius (filled blue points) and between the
virial and baryon radius (open red points).  {\bf All fractions are
  relative to the fiducial baryonic mass within the  virial radius}.
%
The fractions of cold gas, $f_{\rm cold}$, are shown in the left
panel.  Inside the virial radius $f_{\rm cold}$ increases gradually
from zero at a halo mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo
mass of $10^{12}\Msun$.  The gas outside the virial radius has the
opposite and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of
mass $10^{10}\Msun$ and decreases to zero by halo masses of
$10^{11}\Msun$.
%
The fractions of cool gas, $f_{\rm cool}$, are shown in the middle
panel.  Inside the virial radius, $f_{\rm cool}$, has a maximum of
40\% at a halo mass of $10^{11} \Msun$, and declines to less than 10\%
below and above halo masses of $10^{10}\Msun$ and $10^{12}\Msun$,
respectively.  For most haloes there is more cool gas outside than
inside the virial radius.  In haloes of mass $10^{10}\Msun$, $f_{\rm
  cool}\sim 80\%$, and decreases to less than 10\% by a halo mass of
$10^{12}\Msun$.
%
The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
right panel.  The trends of the gas inside and outside the virial
radius are quite similar, $f_{\rm warm}$ increases monotonically with
halo mass with maximum values of $\sim 30\%$.
%
The hot gas isn't shown since it is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo masses in the range
$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
associated with the dark matter halo are in the cold and cool phases,
and are located well outside of virial radius.  For haloes in the mass
range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
gas, cool gas and  warm-hot gas are comparable.

@@

The COS-HALOs survey is filling in details about the CGM at low
redshift \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13,
  Werk14}.  For the CGM of low-redshift $\sim L^*$ galaxies
($\Mstar\sim 10^{10.5}\Msun$), \citet{Tumlinson13} and
\citet{Peeples14} constrain the mass of  the warm-hot CGM ($T \sim
10^{5-6.7}$K), \citet{Werk14} provides a strict lower limit to the
mass of cool material ($T \sim 10^{4-5}$K) in the CGM of these
galaxies.  In a study using X-rays, \citet{Anderson13} place a
constraints on the mass of  hot gas ($T > 5\times10^6$K) residing in
the extended hot halos.  These observational constraints are shown in
Fig.~\ref{fig:comparison} with the same colour scheme as in Fig.11 of
\citet{Werk14}.  The stellar mass fractions are based on halo
abundance matching as described in \citet{Kravtsov14}, while the cold
disk gas mass comes from \citet{Dutton11}.  {\bf The upper limits to
  the missing fraction are calculated using the lower limits to all
  the fractions. There are two upper limits shown which correspond to
  the two measurements of the cool-gas fraction
  \citep{Werk14,Stern16}. The lower limit to the missing fraction is
  consistent with zero.}

%% FIGURE 7
\begin{figure*}
\centerline{
  \psfig{figure=budget.eps,width=0.8\textwidth}
}
\caption{Baryonic budget  of NIHAO haloes of mass $3.5\times 10^{11} <
  M_{200}/\Msun < 3.5 \times 10^{12}$ (black points  with 1$\sigma$
  error bars) compared with observations of  $M_{200} \sim
  10^{12}\Msun$ haloes (shaded regions). There is good agreement,
  except for the cool gas which has two conflicting measurements:
  \citet[][upper]{Werk14} upper, \citet[][lower hatched]{Stern16}.  }
\label{fig:comparison}
\end{figure*}

The black points and error bars show the mean values and standard
deviation of the mass fraction of stars and different components of
gas in our most massive galaxies ($3.49 \times 10^{11} \Msun$ $<$
M$_{200}$ $<$  $3.53 \times 10^{12} \Msun$).  The gas is assigned to a
range of temperature bins:  cold gas (T $< 10^4$ K), cool gas ($10^4$
K $<$ T $< 10^5$ K),  warm gas ($10^5$ K $<$ T $<5\times 10^6$ K) and hot gas
(T $>5\times 10^6$ K).  The observations and the simulations match well in
every phase except the cool CGM gas, where the observations from
\citet{Werk14} find $3\times$ the mass that NIHAO simulations predict.
